Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-03-18 answer-to-reviewers.tex

\smallskip

\emph{The other paper Reviewer 1 mentions here is:}

\nocite{2016:walter-coolen}
\bibliographystyle{elsarticle-harv}
\bibliography{refs}
\smallskip

\emph{We cite this paper in our manuscript in Section~4,
clearly stating, in the last paragraph before Section~4.1,
that our manuscript and the cited paper share the same basic approach, namely
Weibull component models with conjugate inverse Gamma prior
combined with a survival signature approach to calculate the system remaining life distribution (RLD).
As mentioned there, however, the focus of these two works is entirely different.
The cited paper develops an approach to use \textbf{sets} of inverse Gamma priors,
to allow for a sophisticated modeling of uncertainties in the component models,
resulting in \textbf{sets} of RLDs which are the ultimate result of the paper.
Instead, the present manuscript uses the basic approach to develop a \textbf{maintenance policy},
using \textbf{a single} RLD as input for an optimization of the mean cost rate to find the cost-optimal moment of system maintenance.
Sections~4.1 to 4.3 describe the approach used for RLD calculation
in a similar way than the cited paper,
but with notation adapted to the manuscript's objective, i.e., defining a maintenance policy.
For readers to be able to understand our approach,
we considered it necessary to include a detailed description of the RLD calculation,
and not just refering to the paper.
}

@@

\medskip

I have the following questions that I hope the authors can answer.\\
Questions:
\begin{enumerate}
\item In cases of pessimistic and optimistic priors, should we continually update or do not update component reliability in terms of minimizing the overall cos[t]?

\smallskip

\emph{In both cases, it is optimal to continually update the component model parameters.
This is exemplarily shown in the case study in Section~6, with more systematic evidence given in Section~7.
In Section~6.2, the case of failures happening later than expected, i.e., a pessimistic prior is considered,
and the last paragraph before Section~6.3 (beginning with ``The effect of the continuous parameter update \ldots'')
gives a detailed explanation.
Section~6.3 studies a case with failure times earlier than expected, i.e., with too optimistic prior.
Here, as described in the text, both the approach with and without continuous parameter update
trigger maintenance at the same time, leading to the same costs.
However, Figure~8 shows that without continuous parameter update, the system RLD is overestimated,
which may lead to an excess risk of system failure.
This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
than the approach without continuous parameter update (CBM-epu and CBM-npu).
Citing the last sentence of Section~7,
``[o]verall, it seems that CBM-cpu can play its adaptive strengths most effectively
when prior assumptions are too pessimistic,
while also performing well when prior assumptions are correct or too optimistic.''\\
***change some wording?***\\
***impossible to know beforehand if priors too optimistic or too pessimistic***}
%
\item For the example system, I think we can simply use the key stone method (use H as the key stone) to calculate the system reliability when the components are independent.  Is it necessary to use system signature?

@@

\smallskip

\emph{The example system was deliberately chosen to be very simple,
and for such a system, indeed a simpler methodology like the keystone method could very well suffice.
However, our survival signature based method is also applicable for larger systems where the keystone method
is not applicable or cumbersome.
Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to easily calculate the
survival signature from a given system graph.\\
%no one component can be singled out as the reliability-limiting force.\\
***add a note on simplicity at example intro in Section~3?***\\
***use more complex system for simulation study?***}
\end{enumerate}

@@

\emph{***We need to add a comment on this in Section~8. It is possible to have costs dependent on time and on system state,
method works in the same way, $\tausnow$ will be more variable then.
Relation to our simplifying assumption that all components are replaced in a maintenance action?***}

\item Throughout the manuscript it is assumed that the survival signature, $\Phi$, is a given parameter of the problem and no further details are given. Even though this may be correct for any real life application of their methodology, for the sake of completeness I will suggest to either include the complete version of Table 1 (maybe as an appendix) or to provide a closed form of the corresponding survival signature for their toy example.

\smallskip

\emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
and would like to apologize for the confusion that these errors may have caused.
We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.}
%{\scriptsize
%(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
%If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
%(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
%If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
%Also add complete table in Appendix, or formula for $\Phi$ based on structure function???
%Also note here that there is software to calculate $\Phi$?***}

@@

\item Five subsequent operation cycles seems to be a rather short simulation horizon. I will suggest the authors to extend their analysis to, at least, 20-25 cycles.

\smallskip

\emph{***??? We can do more subsequent operation cycles,
but I would think more repetitions (say, 50 or 100 instead of 20) would be better.
Maybe emphasize that we use a single-cycle optimization criterion,
not a renewal-based criterion that indeed holds only for a large number of cycles?
Also, for many cycles the difference between CBM-cpu and CBM-epu will decrease.***}

@@

\subsection*{General Comments}

\begin{enumerate}
\item The authors claim that no degradation signal is used for monitoring the system’s state. However, they mention that the status of the components can be monitored continuously. How can this be done? This question becomes more important when the authors mention that certain inspections (which reveal the status of the systems) can be conducted periodically. This seems to be in contradiction with the continuous monitoring mentioned above. Could the authors be so kind to clarify this?

\smallskip

\emph{***??? It seems we have confused the reviewer thoroughly.
We need to clarify that we do not use a \textbf{usual} degradation signal, like vibration measurements.
But we do get a (time-) continuous signal from the components of the system, telling us whether they work or not.
I need to check again if we say somewhere that we do inspections periodically, which is not true.
We re-evaluate the RLD periodically (and additionally at times of component failures).***}

@@

\emph{*** Section~4.1 introduces the Weibull component models
and the conjugate inverse Gamma prior distribution in our non-standard parametrization,
explaining the Bayesian parameter update step for right-censored lifetimes.
We think that Section~4.1 is crucial to the understanding of our method,
especially for readers not familiar with Bayesian approaches.
As mentioned in our answer to Reviewer~1's main comment,
Sections~4.1 to 4.3 combine results from several parts of the cited manuscript
in a form that is adapted to the purpose of the present manuscript.
We thus think that it is preferable to keep Section~4.1 within the main part of the manuscript.}

\item I suggest to place Figure 2 somewhere after parameters $m$ and $\delta$ are defined and the maintenance policy is described in Section 5.1 (for example at the end of the section). Otherwise, it is hard to follow.

\smallskip

\emph{We had placed Figure~2 (depicting the flowchat for the policy, now Figure~3) directly before Section~5.1 which explains the policy,
and agree that it should appear during or after Section~5.1 to avoid confusion.***}

@@

\item A timeline sketch depicting the evolution of the policy on time, where the different elements of a time grid are illustrated, will be welcome.

\smallskip

\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~2.}

@@

The weak point of the work is related to the different hypothesis which significantly simplify the modeling framework. More precisely:

\begin{enumerate}
\item All the components have the same lifetime model (namely the Weibull distribution) with a known fixed shape parameter which is not discussed. Only the scale parameter is updated and directly associated with the mean lifetime if the shape parameter is known.

\smallskip

\emph{We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
We added a comment on this in the conclusion,
repeating a comment from the beginning of Section~4, where we wrote:
``The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by Soland (1969).''
We now also emphasize in the introduction and the conclusion that the proposed method should be seen as a first step towards
a completely new class of CBM policies.***}

@@

\item In the introduction the authors claim that ``the system RLD does not require a physical inspection’’ because the failure time of each component is detected online via continuous monitoring. This hypothesis seems to be very strong as it requires a costly related instrumentation. Most of the time, systems with redundancies are not monitored in a such way. if a specific application field is inferred, please give it explicitly. It could be interesting to discuss shortly the sensitivity of the proposed maintenance policy to non-detection of some components failures.

\smallskip

\emph{***We have added a short discussion related to the non-detection of component failures in the conclusion.
We were mostly thinking of systems where a failure of a component is immediately eminent,
but the measurement of the component's health degree is very difficult or too costly.
This is, e.g., the case for components in power systems, where failure of a certain component
is usually reflected in a loss of current (detectable from the control centre),
but proper health monitoring (going beyond working yes/no) is cumbersome and costly.
***}

@@

\item The maintenance of the system is always a replacement of the whole system by an as good as new one. This hypothesis is hard to accept especially if all the components are continuously monitored.

\smallskip

\emph{***Agreed, this is another important simplifying assumption that we needed to make in this manuscript,
which should be seen as a first step towards a completely new class of CBM policies.
We originally mentioned this in the description of the policy but only at the end of Section~5.1,
and commented on this in the fourth paragraph of the conclusion (Section~8), bottom of p.~25.
In the introduction and the complete re-write of Section~5, we tried to emphasize the pilot character of our approach,
mentioning the restricting assumptions more prominently.***}
\end{enumerate}

@@

\emph{Agreed, we deleted that notion, and hope to be more clear now here.***}

\item Page 2, line 15 from bottom: Please explain the acronym ``RLD’’ the first time it is used.

\smallskip

\emph{We are sorry that we defined RLD too late, and now define it at first use.}

@@

\emph{Agreed, the respective sections are now added.}

\item Page 7: The choice of the inverse Gamma distribution as a prior is interesting for mathematical reasons. Are there some possible tests to justify this choice from data?

\smallskip

\emph{It is not possible to use data for testing the adequacy of the parametric family of the prior,
as it is supposed to reflect the expert's opinion.
So the crucial question is rather whether inverse Gamma distributions can adequately reflect the expert's opinions.
A tool to help answering that question are prior predictive distributions.
They give a distribution for the failure times that can be expected according to the expert's choice of prior
(here: inverse Gamma with specific parameters)
\textbf{in combination with the assumed sample model} (here: Weibull).
Figure~6 (previously Figure~5)*** depicts prior predictive reliability functions for the priors in the case study of Section~6,
as a way to visualize the choice of prior parameters given in Table~2 in the context of the Weibull model.
When an expert feels that these prior predictive reliability functions do not correspond to the failure time distribution (s)he postulates,
and no change of prior parameters can approximate the postulated failure time distribution,
then the prior family would seem inappropriate,
under the condition that the sample model is indeed correct.
(Methods for checking the sample model are discussed, e.g., in
Bayarri and Berger (2000), ``P values for composite null models'',
Journal of the American Statistical Association 95(452): 1127–1142.)\\
***add this reference to the paper?***}

@@

\emph{***depends on the scale of failure times? seconds / minutes? ??? not sure what is meant by the second sentence.}

\item Page 14, first paragraph: Is it possible to determine the number of operational cycles which is necessary to improve significantly the values of the parameters? It seems that after a certain amount of time the updates will have a negligible effect.

\smallskip

\emph{***Indeed, after a certain time the parameter $y_k$ (the expected value of the Weibull scale parameter $\lambda_k$)
will not change by much during the update in Equation (7).
However, the strength parameter $n_k$ will continue to increase,
since the other part of (7) reads $n'_k = n_k + e_k$, i.e.,
$n_k$ is incremented by 1 for each observed failure.
The consequence is that the posterior distribution over $\lambda_k$ becomes ever more pointed
(the variance of the posterior approaches zero),
such that the posterior predictive distribution approaches the Weibull distribution with $\lambda_k$ equal to $y_k$.
Stopping to update would make only sense when the posterior is practically equal to a point mass on $y_k$.
However, this holds only if a component's failure behaviour does not change.
Updating allows to automatically adapt to any changes in the failure behaviour.}

### 2017-03-18 cbm-rbd-paper.tex
further tweaks, sending to SDF now

Continuing our example,
the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
because the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.

@@

>>>>

Continuing our example,
the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
because the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
***The omitted rows from Table~\ref{tab:brakesys-survsign} can be determined as follows:
\begin{itemize}
\item Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $0$.
\item Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $1$.
\end{itemize} 
***As an example, Consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
i.e., $M$ has failed, $H$ functions, $C_1$ -- $C_4$ have failed, and one of $P_1$ -- $P_4$ functions.
The system functions only if the single functioning type $P$ component is either $P_3$ or $P_4$.
As the type $P$ components are exchangeable, each has the same probability of being the functioning component,
and so the probability of $P_3$ or $P_4$ being the functioning component is $0.5$, and $\Phi(0, 1, 0, 1) = 0.5$.

The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
provides a convenient function to calculate the survival signature based on a given graph.

@@

***different cost structures, let repair costs depend on number of failed components?***
